Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-03 SWoPP2018 Paper/paper.tex
Added a reference

The present paper focuses on the IEEE-754 part of inference, where training and alternative data-types are on-going and future work.

@@

The performance is memory bandwidth limited for these kernels.

@@

>>>>

The present paper focuses on the IEEE-754 part of inference, where training and alternative data-types are on-going and future work. Althought we do have a posit~\cite{podobasposit} generator ready to be used, it has yet to be integrated into our flow.

@@

The performance is memory-bound for these kernels. However, given our experience with alterantive numerical formats (most noticable posits~\cite{podobasposit}), we do not expect performance to be degraded when changing numerical format.

@@

\bibitem{podobasposit}
  Podobas, Artur and Matsuoka, Satoshi:  
  Hardware Implementation of POSITs and their application in FPGAs
  {\it International Parallel and Distributed Processing Symposium Workshops},
  to appear, 2018
